---
output:
  html_document: default
  pdf_document: default
---
# Lab Exercise-3 (Essentials of Data Analytics)
### Karthik Kurella
### 17MIS1022
### Date : 22-Feb-2021

Steps to follow:

1. Make sure that the dataset can be described using additve model. i.e, seasonality and random fluctuations should remains constant in size over time. if not transform data using 'log'.

2. decomposing time series - separating into constituent components - trend , random , seasonal(if data is seasonal).


Decomposing non-seasonal data

- moving average method - Smoothing method - SMA(data , n = ) - TTR Package
if we still have any random fluctuations in the data try increasing n value.

Decomposing Seasonal data

- decompose command in r
here we can deseasonalise the data by substracting the decomposed data with the original(data - decomposed_data$seasonal).

3. make predictions
```{r,echo=FALSE}
library(astsa, quietly=TRUE, warn.conflicts=FALSE)
library(ggplot2)
library(knitr)
library(printr)
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(gridExtra)
library(reshape2)
library(TTR)
library(tseries)
library(forecast)
library(ggfortify)
library(caret)
```

```{r}
#data()

data_master <- read.csv("E:/Sems/sem-8/essentials of data analytics/lab/GSPC.csv")
str(data_master)
```
```{r}
sp_500 <- ts(data_master$High, start=c(1995, 1),end = c(2016,12), freq=12)
summary(sp_500)
sp_500
plot.ts(sp_500)
plot(sp_500,xlab="Date", ylab = "Passenger numbers (1000's)",main="Air Passenger numbers from 1949 to 1961")

```

```{r}
boxplot(sp_500~cycle(sp_500),xlab="Date", ylab = "Closing price of the stock market" ,main ="Monthly closing price ")
```
```{r}
decompose_data = decompose(sp_500,"multiplicative")
plot(decompose_data)
```

```{r}
adf.test(sp_500)
autoplot(acf(sp_500,plot=FALSE))+ labs(title="Correlogram from 1995 to 2015") 

```

```{r}
sp500SMA<- SMA(sp_500, n=3)
plot.ts(sp500SMA)
```

```{r}
sp_500
summary(sp_500)
cycle(sp_500)
#autoplot(sp_500) + geom_smooth(method="lm")+ labs(x ="Date", y ="Open", title="air")
class(sp_500)
sum(is.na(sp_500))

```
```{r}
plot.ts(sp_500)+abline(reg=lm(sp_500~time(sp_500)),col="blue")
```

```{r}
arimaAP <- auto.arima(sp_500)
summary(arimaAP)
```
* Finally we can plot a forecast of the time series using the forecast function, again from the forecast R package, with a 90% confidence interval where h is the forecast horizon periods in months.
```{r}
forecastAP <- forecast(arimaAP, level = c(90), h = 12)
autoplot(forecastAP)
```




