---
output:
  html_document: default
  pdf_document: default
---
# Lab Exercise-4 (Essentials of Data Analytics)
### Karthik Kurella
### 17MIS1022
### Date : 22-Feb-2021

```{r,echo=FALSE}
library(ISLR)
library(corrplot)
library(dplyr)
library(caret)

```
* Logistic Regression
* Logistic regression is another technique by machine learning.It measures the relationship between the categorical dependent variable and one or more independent variables by estimating probabilities using a logistic function, which is the cumulative logistic distribution.
```{r}
#data()
names(Smarket)
head(Smarket)
```
* Exploring Data:
* Let's explore it for a bit. names() is useful for seeing what's on the data frame, head() is a glimpse of the first few rows, and summary() is also useful.
```{r}
summary(Smarket)

```
* Correlation
* Calculating the correlation between each pair of numeric variables. These pair-wise correlations can be plotted in a correlation matrix plot to given an idea of which variables change together.

```{r}

correlations <- cor(Smarket[,1:8])
corrplot(correlations, method="circle")
```
```{r}
training.samples <- Smarket$Direction %>% createDataPartition(p = 0.8, list = FALSE)
train <- Smarket[training.samples, ]
test <- Smarket[-training.samples, ]
```

```{r}
model_glm <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data = train, family = binomial)
```

```{r}
summary(model_glm)
```

* Predictions and Confusion Matrix

```{r}
glm.probs <- predict(model_glm,type = "response")
table(train$Direction, glm.probs > 0.5)

```
* GGplot Curve

```{r}
library(ggplot2)
ggplot(train, aes(x=Lag1, y=Direction)) + geom_point() + 
stat_smooth(method="glm", family="binomial", se=FALSE)
```

