---
output:
  html_document: default
  pdf_document: default
---
# Lab Exercise-5 (Essentials of Data Analytics)
### Karthik Kurella
### 17MIS1022
### Date : 03-March-2021

```{r,echo=FALSE}
library(ggplot2) # Data visualization
library(rpart)
library(rpart.plot)
library(rattle)
library(tree)
```

* Importing the dataset
```{r}
data <- read.csv("bank.csv",sep = ";")
idx <- sample(1:nrow(data),8)
sapply(data, class)
head(data)
glimpse(data)
```
* Data cleaning
* Create numerical variables for feature matrix
* Drop the NA
```{r}
data$age <- as.numeric(data$age)
data$balance <- as.numeric(data$balance)
data$day <- as.numeric(data$day)
data$duration <- as.numeric(data$duration)
data$campaign <- as.numeric(data$campaign)
data$pdays <- as.numeric(data$pdays)
data$previous <- as.numeric(data$previous)
```

* Create train/test set
* Before we train your model, we need to :

* Create a train and test set: 
```{r}
size <- nrow(data) * 0.8
temo<-na.omit(data)
data_bank <- sample(1:nrow(data), size = size)
data_testing <- data[-data_bank,]	# Testing Data
data_training <- data[data_bank,]		# Training Data
summary(data_training)
prop.table(table(data_training$y))
```

```{r}
data_training.rpart <- rpart(y ~ ., data = data_training)
fancyRpartPlot(data_training.rpart)
predict_unseen <-predict(data_training.rpart, data_testing, type = 'class')

table_mat <- table(data_testing$y, predict_unseen)
table_mat

accuracy_Test <- sum(diag(table_mat)) / sum(table_mat)
print(paste('Accuracy for test', accuracy_Test))

```
* Conclusion
* we start at the root node (depth 0 over 3, the top of the graph):

* At the top, it is the overall probability of y. It shows the proportion of y that makes  the loan. 51 percent of passenger survived.
* one of the many qualities of Decision Trees is that they require very little data preparation. In particular, they don't require feature scaling or centering.
* The model correctly predicted 774 loaned customers but classified 38 are rejected. By analogy, the model misclassified 68 observations as obtained loan while they turned out to be obtained the loans.
* Score of 90 percent for the test set