#### Essentials of Data Analytics - LAB3
#### 17MIS1020 - Karthik Prasad
#### Time series Data



Steps to follow:

1. Make sure that the dataset can be described using additve model. i.e, seasonality and random fluctuations should remains constant in size over time. if not transform data using 'log'.

2. decomposing time series - separating into constituent components - trend , random , seasonal(if data is seasonal).


Decomposing non-seasonal data

- moving average method - Smoothing method - SMA(data , n = ) - TTR Package
if we still have any random fluctuations in the data try increasing n value.

Decomposing Seasonal data

- decompose command in r
here we can deseasonalise the data by substracting the decomposed data with the original(data - decomposed_data$seasonal).

3. make predictions
 

```{r}
library(astsa, quietly=TRUE, warn.conflicts=FALSE)
library(ggplot2)
library(knitr)
library(printr)
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(gridExtra)
library(reshape2)
library(TTR)
library(tseries)
library(forecast)
library(ggfortify)

```


```{r}
df = read.csv("rainfall_1901-2015.csv")
str(df)
head(df)
```


```{r}
#extracting rainfall details in telangana state

telangana <-df%>%filter(SUBDIVISION=="TELANGANA" & YEAR %in% c(1910:1920))%>%group_by(SUBDIVISION,YEAR) 


telangana=telangana[,-c(1,15,16,17,18,19)]

head(telangana)
nrow(telangana)
telangana = telangana %>%
  pivot_longer(!YEAR, names_to = "month", values_to = "Rain")


nrow(telangana)

telangana
data = ts(telangana[,3],frequency = 12,start = c(1910,1))

head(data)

plot.ts(data)
#plot.ts(log(data))

boxplot(data~cycle(data),xlab="Date", ylab = "Rain" ,main ="Monthly Rainfall Boxplot from 1901 to 1950")

```


```{r}
decompose_data = decompose(data,"multiplicative")
plot(decompose_data)

#testing for stationary

adf.test(data) 


```

```{r}
autoplot(data) + geom_smooth(method="lm")+ labs(x ="Date", y = "Passenger numbers (1000's)", title="Air Passengers from 1949 to 1961")


arima_data <- auto.arima(data)
arima_data

ggtsdiag(arima_data)

forecast_data <- forecast(arima_data, level = c(95), h = 36)
autoplot(forecast_data)

```


```{r}
final <- SMA(rainSeasonAdj, n=6)
plot.ts(final)

```


```{r}
```


```{r}
```

```{r}
```


```{r}
```


```{r}
```


```{r}
```

